\documentclass{article} 
\usepackage{comment}
\usepackage{hyperref}
%\usepackage[a4paper, margin=2.5cm]{geometry}
\usepackage{geometry}
\geometry{a4paper,left=.8in,right=.8in,top=.8in,bottom=.8in}
\usepackage{cite}
\usepackage[utf8]{inputenc}
%%%%%%%%%%%%%%%%%%%%
\input{resCommands}
\renewcommand\refname{List of Publications}
%%%%%%%%%%%%%%%%%%%%
%\setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

\begin{document} 
\begin{center}
	\Large{\bf \name}
\end{center}
%{\bf  PRESENT ADDRESS\\Dept. Of CSE\\IIT Guwahati\\Assam India-7810398}
%\address{\bf PERMANENT ADDRESS \\ Rail Bazar \\Beldanga, Murshidabad\\  West Bengal India-742189}
%\address{\bf \\Email: \\ subhrendu@iitg.ernet.in}
%                                  
%\begin{resume}

%	\begin{table}[h]
%	\centering
%	\begin{tabular}{|ll|l|}
%	\hline
%	\multicolumn{2}{|c|}{\bf Address:}            								&	\multicolumn{1}{|c|}{\bf Email:}               \\
%	%{\bf Present Address:}    & {\bf Permanent Address:}        	&	{\bf Email:}               \\
%	 \multicolumn{2}{|l|}{c/o Subhas Ch. Chattopadhyay,} 			&	subhrendu.subho@gmail.com         \\\cline{3-3}
%	 \multicolumn{2}{|l|}{55, Charichara Bazar Lane} 					&	\multicolumn{1}{|c|}{\bf Mobile:}  \\
%	 \multicolumn{2}{|l|}{Nabadwip, Nadia} 									&	+91-9435658234, +91-8918796261  \\
%  	\multicolumn{2}{|l|}{ Westbengal, India 741302}					&	\\\cline{1-3}
%  	\multicolumn{2}{|l|}{\bf Website:}											& 	\multicolumn{1}{|c|}{\bf Skype:}  \\
%	\multicolumn{2}{|l|}{https://subhrendu1987.github.io/}			&	 live:subhrendu.subho_1 \\ \hline
%	\end{tabular}
%	\end{table}
 \noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\section{Contact Information}
	\begin{itemize}
		\item {\bf Address:} c/o Subhas Ch. Chattopadhyay, 55-Charichara Bazar Lane, Nabadwip, Nadia, Westbengal, India 741302
		\item {\bf Website:} \url{https://subhrendu1987.github.io/}
		\item {\bf Email:} subhrendu.subho@gmail.com
		\item {\bf Mobile:} +91-9435~658~234, +91-8473894164
		\item {\bf Skype:} live:subhrendu.subho\_1
	\end{itemize}
\section{Current Position}          
Temporary 	Project Staff
Department of Computer Science and Engineering (From October 2020)\\
Indian Institute of Technology, Kharagpur\\
Project Name: Development of Algorithms and Tools for Log Analytics  and Vulnerability Assessment \\
Principal Investigator: Dr. Sandip Chakraborty
<<<<<<< HEAD
\section{Previous Position}
	Ph.D. Research Scholar  (From July 2014- September 2020)\\
    Department of Computer Science and Engineering\\
    Indian Institute of Technology, Guwahati\\
    Thesis Title: SDN for Large Scale IoT Networks\\
    Supervisor: Prof. Sukumar Nandi
=======
>>>>>>> 0745444c397078eb90b6980017c713cb4c2c6b5c
\section{Area of Interests}    
 		My research interests include Software Defined Networking, Fog Computing, Next Generation Wireless Networks, Distributed Algorithms and Performance Modeling of Network and Communication System.
\section{Academic Qualification} 
	{\bf Post Graduation:} Doctor of Philosophy in Computer Science and Engineering from Indian Institute of Technology, Guwahati (July 2014 - April 2021)\\[3ex]
	{\bf Post Graduation:} Master of Technology in Computer Science and Engineering with {\bf CGPA: 8.81/10} from Indian Institute of Technology, Guwahati (June 2012 - July 2014)\\[3ex]
	{\bf Graduation:}Bachelor of Technology in Computer Science and Engineering with {\bf CGPA: 8.04/10} from B.P Poddar Institute of Management and Technology, WestBengal University of Technology (July 2006 - June 2010)\\[3ex]
	{\bf Higher Secondary (10+2):} with {\bf 77.5\%} from Beldanga C.R.G.S High School, under West Bengal Council of Higher Secondary Examination (May, 2006)\\[3ex]
	{\bf Secondary (10):} Madhyamik with {\bf 81.5\%} from Sargachhi Ramakarishna Mission High School, under West Bengal Board of Secondary Education (April, 2003)
\section{Awards}
	\begin{enumerate}
		\item{\bf Fellowship:} Recipient of TCS Research scholarship (Cycle 10) and Fellowship from MHRD
		\item {\bf Travel Grants:} 
			\begin{enumerate}
				\item Received conference travel grant from IEEE COMSNETS and LRN foundation.
				\item Recipient of travel grant from Mirosoft India, Research and Development
			\end{enumerate}
		\item {\bf Best paper awards:} 
			\begin{enumerate}
				\item IEEE INFOCOM 2019~\cite{chattopadhyay2018aloe} (in a session)
				\item IEEE COMSNETS 2016~\cite{chakraborty2016es2}
				\item IEEE ANTS 2013~\cite{chakraborty2013surpassing}
			\end{enumerate}
	\end{enumerate}
\section{Teaching Assistance}	
	\begin{enumerate}
	 \item {\bf Teaching Assistant} in IIT, Guwahati For Operating Systems (CS341) (2018 Monsoon)
	 \item {\bf Teaching Assistant} in IIT, Guwahati For Network Lab (CS343) (2016 Monsoon)
	 \item {\bf Teaching Assistant} in IIT, Guwahati For Wireless Networks (CS551) (2015 Monsoon, 2017 Monsoon)
	 \item {\bf Teaching Assistant} in IIT, Guwahati For Systems Lab (CS558) (2014 Winter,2015 Winter,2016 Winter,2018 Winter)
	 \item {\bf Teaching Assistant} in IIT, Guwahati For Programming Lab (CS513) (2013 Monsoon, 2014 Monsoon)
	 \item {\bf Teaching Assistant} in IIT, Guwahati For Computing Laboratory (CS110) (2013 Winter)
	 \item {\bf Teaching Assistant} in IIT, Guwahati For Discrete Mathematics (CS202)  (2012 Monsoon)
	\end{enumerate}
\section{Professional Experience}
	{\bf Automation Test Engineer:} Programmer Analyst Trainee in Cognizant Technology Solution India Pvt. Ltd. (July 2010 - July 2011)\\[3ex]
	{\bf Professional Certification:} LOMA 280 certified with 99.2\%         
\section{Voluntary Services}
  \begin{enumerate}
   \item Conference Reviewer: IEEE ANTS (2014 - 2018), IEEE ICC 2017, IEEE NCC 2017, IEEE ISED 2017, IEEE COMSNETS (2018-2019)
   \item Journal Reviewer: Springer Journal of Network and Systems Management
   \item Member of Technical Program Committee: IEEE  COMSNETS (2020-2021)
  \end{enumerate}
\section{Collaborations}
I had the opportunity to collaborate with the following distinguished faculty members.
  \begin{enumerate}
  	\item Dr. Sandip Chakraborty, Assistant Professor, IIT Kharagpur
	\item Prof. Soumya K Ghosh, Professor, IIT Kharagpur
	\item Dr. Samar Shailendra, Scientist, TCS Networks Lab
	\item Dr. Sushanta Karmakar, Associate Professor, IIT Guwahati
	\item Dr. Abhinandan S. Prasad, Associate Professor, NIE Mysore
	\item Dr. Debarati Sen, Associate Professor, IIT Kharagpur
	\item Dr. Niladri Sett, Assistant Professor, SRM University AP
  \end{enumerate}
\section{Reference Persons}
  \begin{enumerate}
  \item Prof. Sukumar Nandi, Senior Professor\\Department of CSE, IIT Guwahati, Assam, India-781039, sukumar@iitg.ac.in, (+91~361~258~2357)
  \item Dr. Sandip Chakraborty, Assistant Professor\\Department of CSE, IIT Kharagpur, West Bengal, India-721302, sandipc@cse.iitkgp.ac.in, (+91~322~228~2898)
  \item Prof. Soumya Kanti Ghosh, Professor\\Department of CSE, IIT Kharagpur, West Bengal, India-721302, skg@cse.iitkgp.ac.in, (+91~322~228~2332)
  \end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \nocite{*}
  \bibliographystyle{plainyr-rev}
  \bibliography{mypub}
%\end{resume}

\end{document}
