\documentclass{article} 
\usepackage{comment}
\usepackage{hyperref}
%\usepackage[a4paper, margin=2.5cm]{geometry}
\usepackage{geometry}
\geometry{a4paper,left=.8in,right=.8in,top=.8in,bottom=.8in}
\usepackage{cite}
\usepackage[utf8]{inputenc}
%%%%%%%%%%%%%%%%%%%%
\input{resCommands}
\renewcommand{\thesection}{\Alph{section}}
\renewcommand\refname{List of Publications}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document} 
\begin{center}
	\Large{\bf \name}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Reference Persons}
  \begin{enumerate}
  \item Prof. Sukumar Nandi, Senior Professor\\Department of CSE, IIT Guwahati, Assam, India-781039, sukumar@iitg.ac.in, (+91~361~258~2357)
  \item Dr. Sandip Chakraborty, Assistant Professor\\Department of CSE, IIT Kharagpur, West Bengal, India-721302, sandipc@cse.iitkgp.ac.in, (+91~322~228~2898)
  \item Prof. Soumya Kanti Ghosh, Professor\\Department of CSE, IIT Kharagpur, West Bengal, India-721302, skg@cse.iitkgp.ac.in, (+91~322~228~2332)
  \end{enumerate}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Collaborations}
I had the opportunity to collaborate with the following distinguished faculty members.
  \begin{enumerate}
  	\item Dr. Sandip Chakraborty, Assistant Professor, IIT Kharagpur
	\item Prof. Soumya K Ghosh, Professor, IIT Kharagpur
	\item Dr. Samar Shailendra, Scientist, TCS Networks Lab
	\item Dr. Sushanta Karmakar, Associate Professor, IIT Guwahati
	\item Dr. Abhinandan S. Prasad, Associate Professor, NIE Mysore
	\item Dr. Debarati Sen, Associate Professor, IIT Kharagpur
	\item Dr. Niladri Sett, Assistant Professor, SRM University AP
  \end{enumerate}

\end{document}